Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-12-19 presentations/illustrations/local-prevention.tex
Clarify attack 3 in local setting.

    \begin{scope}
      \fill[gray!50] (13,0) rectangle (18,13);
      \draw (13,0) -- (13,13);
      \draw (18,0) -- (18,13);
      \draw (15.5,14) node {heap memory};
    \end{scope}

    \begin{onlyenv}<+->
      \actsf{(0,2.5)}{(6,5.5)}{caller stack frame}
      \draw[fill=white] (13,1) rectangle (18,3) node[pos=.5] {\footnotesize caller code};
    \end{onlyenv}

@@

    \begin{onlyenv}<+->
      \inactsf{(0,2.5)}{(6,5.5)}{caller stack frame}
      \draw[fill=gray!30] (13,1) rectangle (18,3) node[pos=.5] {\footnotesize caller code};
      \draw[fill=white] (13,4) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
      \actadv{(0,5.5)}{(6,8.5)}{callee stack frame}
    \end{onlyenv}

\note{Callee cannot store ret-ptr on the heap as it is local!}
    \begin{onlyenv}<+-.(2)>
      \draw (13,4.75) edge[red,bend right,thick,->] (ret1);
    \end{onlyenv}

    \begin{onlyenv}<+>
      \draw[teal,very thick] (9,4.9) -- (12.5,5.9);
      \draw[teal,very thick] (9,5.9) -- (12.5,4.9);
      \draw node[teal,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white] () at (14,10) {Return pointer is local!};  
    \end{onlyenv}

@@

    \begin{onlyenv}<+->
      \inactsf{(0,2.5)}{(6,5.5)}{caller stack frame}
      \inactadv{(0,5.5)}{(6,8.5)}{callee stack frame}
      \actsf{(0,8.5)}{(6,11.5)}{callee stack frame (1)}
      \draw[fill=gray!30] (13,1) rectangle (18,3) node[pos=.5] {\footnotesize caller code};
      \draw[fill=gray!30] (13,4) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
      \draw[fill=white] (13,7) rectangle (18,9) node[pos=.5] {\footnotesize callee code (1)};
    \end{onlyenv}

@@

    \begin{onlyenv}<+->
      \inactsf{(0,2.5)}{(6,5.5)}{caller stack frame}
      \inactadv{(0,5.5)}{(6,8.5)}{callee stack frame}
      \inactsf{(0,8.5)}{(6,11.5)}{callee stack frame (1)}
      \actadv{(0,11.5)}{(6,14.5)}{callee stack frame (2)}
      \draw[fill=gray!30] (13,1) rectangle (18,3) node[pos=.5] {\footnotesize caller code};
      \draw[fill=gray!30] (13,4) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
      \draw[fill=gray!30] (13,7) rectangle (18,9) node[pos=.5] {\footnotesize callee code (1)};
      \draw[fill=white] (13,10) rectangle (18,12) node[pos=.5] {\footnotesize callee code (2)};
    \end{onlyenv}

>>>>

    \begin{scope}
      \fill[gray!50] (13,4) rectangle (18,14);
      \draw (13,4) -- (13,14);
      \draw (18,4) -- (18,14);
      \draw (15.5,15) node {code memory};
    \end{scope}

    \begin{scope}
      \fill[gray!50] (13,0) rectangle (18,2);
      \draw (13,0) -- (13,2);
      \draw (18,0) -- (18,2);
      \draw (15.5,3) node {heap memory};
    \end{scope}

    \begin{onlyenv}<+->
      \actsf{(0,2.5)}{(6,5.5)}{caller stack frame}
      \draw[fill=white] (13,5) rectangle (18,6.5) node[pos=.5] {\footnotesize caller code};
    \end{onlyenv}

@@

    \begin{onlyenv}<+->
      \inactsf{(0,2.5)}{(6,5.5)}{caller stack frame}
      \draw[fill=gray!30] (13,5) rectangle (18,6.5) node[pos=.5] {\footnotesize caller code};
      \draw[fill=white] (13,7) rectangle (18,8.5) node[pos=.5] {\footnotesize callee code};
      \actadv{(0,5.5)}{(6,8.5)}{callee stack frame}
    \end{onlyenv}

\note{Callee cannot store ret-ptr on the heap as it is local!}
    \begin{onlyenv}<+-.(2)>
      \draw (13,1.5) edge[red,bend right,thick,->] (ret1);
    \end{onlyenv}

    \begin{onlyenv}<+>
      \draw[teal,very thick] (11.3,3) -- (13,2.8);
      \draw[teal,very thick] (11.8,3.7) -- (12.4,2);
      \draw node[teal,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white] () at (14,10) {Return pointer is local!};  
    \end{onlyenv}

@@

    \begin{onlyenv}<+->
      % \inactsf{(0,2.5)}{(6,5.5)}{caller stack frame}
      \inactadv{(0,5.5)}{(6,8.5)}{callee stack frame}
      \actsf{(0,8.5)}{(6,11.5)}{callee stack frame (1)}
      \draw[fill=gray!30] (13,7) rectangle (18,8.5) node[pos=.5] {\footnotesize callee code};
      \draw[fill=white] (13,9) rectangle (18,10.5) node[pos=.5] {\footnotesize callee code (1)};
    \end{onlyenv}

@@

    \begin{onlyenv}<+->
      % \inactsf{(0,2.5)}{(6,5.5)}{caller stack frame}
      % \inactadv{(0,5.5)}{(6,8.5)}{callee stack frame}
      \inactsf{(0,8.5)}{(6,11.5)}{callee stack frame (1)}
      \actadv{(0,11.5)}{(6,14.5)}{callee stack frame (2)}
      \draw[fill=gray!30] (13,9) rectangle (18,10.5) node[pos=.5] {\footnotesize callee code (1)};
      \draw[fill=white] (13,11) rectangle (18,12.5) node[pos=.5] {\footnotesize callee code (2)};
    \end{onlyenv}
